---
title: "Day1_Assignment"
author: "Molecular Biology and Oncology"
date: "2023-01-03"
output:
  html_document: default
  pdf_document: default
---

## Assignment1:

### Assignment **1 (Calculating GC content)**

Calculate GC content.

Here's a short DNA sequence:

`ACAAGATGCCATTGTCCCCCGGCCTCCTGCTGCTGCTGCTCTCCGGGGCCACGGCCACCGCTGCCCTGCCCCTGGAGGG`

`TGGCCCCACCGGCCGAGACAGCGAGCATATGCAGGAAGCGGCAGGAATAAGGAAAAGCAGCCTCCTGACTTTCCTCGCT`

`TGGTGGTTTGAGTGGACCTCCCAGGCCAGTGCCGGGCCCCTCATAGGAGAGGAAGCTCGGGAGGTGGCCAGGCGGCAGG`

`AAGGCGCACCCCCCCAGCAATCCGCGCGCCGGGACAGAATGCCCTGCAGGAACTTCTTCTGGAAGACCTTCTCCTCCTG`

`CAAATAAAACCTCACCCATGAATGCTCACGCAAGTTTAATTACAGACCTGAA`

Write a program that will print out the G and C content of this DNA sequence.

Please clearly answer:

1.  How many G is in this DNA seq?

2.  How many C is in this DNA seq?

3.  What percentages of this DNA seq included G and C?

Hint: you can use normal mathematical symbols like add (+), subtract (-), multiply (\*), divide (/), and parentheses to carry out calculations on numbers in R.

#### Solution1

```{r}
#my_dna <- ...

```

### Assignment 2 (Complementing DNA)

Use DNA sequence from Assignmnet 1:

Write a program that will print the complement of this sequence.

This one seems pretty straightforward -- we need to take our sequence and replace A with T, T with A, C with G, and G with C. We'll have to make four separate calls to replace, and use the return value for each on as the input for the next tone.

#### Solution 2

```{r}

#my_cDNA <- ...
```
