---
title: "D1_Assignment"
author: "Molecular Biology and Oncology"
date: "2023-01-03"
output:
  html_document: 
      code_folding: show
---

## Assignments:

### Assignment **1 (Calculating GC content)**

Calculate GC content.

Here's a short DNA sequence:

'ACAAGATGCCATTGTCCCCCGGCCTCCTGCTGCTGCTGCTCTCCGGGGCCACGGCCACCGCTGCCCTGCCCCTGGAGGGTGGCCCCACCGGCCGAGACAGCGAGCATATGCAGGAAGCGGCAGGAATAAGGAAAAGCAGCCTCCTGACTTTCCTCGCTTGGTGGTTTGAGTGGACCTCCCAGGCCAGTGCCGGGCCCCTCATAGGAGAGGAAGCTCGGGAGGTGGCCAGGCGGCAGGAAGGCGCACCCCCCCAGCAATCCGCGCGCCGGGACAGAATGCCCTGCAGGAACTTCTTCTGGAAGACCTTCTCCTCCTGCAAATAAAACCTCACCCATGAATGCTCACGCAAGTTTAATTACAGACCTGAA'


Write a program that will print out the G and C content of this DNA sequence.

Please clearly answer:

1.  How many G is in this DNA seq?

2.  How many C is in this DNA seq?

3.  How many percentages of this DNA seq included G and C?

Hint: you can use normal mathematical symbols like add (+), subtract (-), multiply (\*), divide (/), and parentheses to carry out calculations on numbers in R.

#### Solution1

```{r, results='hide',include=FALSE, class.source = "fold-show"}
library(tidyverse)
```

```{r, results='hide' ,class.source = 'fold-hide'}
my_dna <- "ACAAGATGCCATTGTCCCCCGGCCTCCTGCTGCTGCTGCTCTCCGGGGCCACGGCCACCGCTGCCCTGCCCCTGGAGGGTGGCCCCACCGGCCGAGACAGCGAGCATATGCAGGAAGCGGCAGGAATAAGGAAAAGCAGCCTCCTGACTTTCCTCGCTTGGTGGTTTGAGTGGACCTCCCAGGCCAGTGCCGGGCCCCTCATAGGAGAGGAAGCTCGGGAGGTGGCCAGGCGGCAGGAAGGCGCACCCCCCCAGCAATCCGCGCGCCGGGACAGAATGCCCTGCAGGAACTTCTTCTGGAAGACCTTCTCCTCCTGCAAATAAAACCTCACCCATGAATGCTCACGCAAGTTTAATTACAGACCTGAA"
dna_count<- str_length(my_dna)

dna_count

G_Counts <- str_count(my_dna, "G")
C_Counts <- str_count(my_dna, "C")
total <- str_length(my_dna)
str_c("Number of G in this DNA is ", G_Counts)
str_c("Number of C in this DNA is ", C_Counts)
# calculating the ratio of A and T in this DNA seq
(G_Counts + C_Counts)/total *100
```

### Assignment 2 (Complementing DNA)

Use DNA sequence from Assignmnet 1:

Write a program that will print the complement of this sequence.

This one seems pretty straightforward -- we need to take our sequence and replace A with T, T with A, C with G, and G with C.

#### Solution2

```{r, results='hide',class.source = 'fold-hide'}

dna <- str_replace_all(my_dna, c("A" = "t", "C" ="g", "G"= "c", "T"= "a"))
toupper(dna)
dna <- toupper(dna)
```
