---
title: "Day2_Practice"
author: "Molecular Biology and Oncology"
date: "2023-01-03"
output:
  html_document: 
      code_folding: show
---




Preparation

```{r, results='hide',include=FALSE, class.source = "fold-show"}
library(tidyverse)
```

## Exercise 2.a:

There are two strings of DNA. How many `ATG`s are in each sequence? Show
them?

`ACATGTCATGTCC` and `CTTGTATGCTG`

### Solution 2.a:

```{r, results='hide' ,class.source = 'fold-hide'}
sequences<-c("ACATGTCATGTCC","CTTGTATGCTG")
str_count(sequences, "ATG")
str_view_all(sequences, "ATG")
```

## Exercise 2.b:

We have three sequence of DNA.

`"ACTGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT"`

`"ACTTGAATTCTTCAGCTGAGATTCGG"`

`"ATCGGGTTAATACGTGAATTCAGGCTGATCGTGTAGCTTGGATCC"`

Write a program to locate the position of the EcorI (GAATTC) Restriction
Enzyme Zone.

### Solution 2.b:

```{r, results='hide' ,class.source = 'fold-hide'}
my_dna <- c("ACTGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT", "ACTTGAATTCTTCAGCTGAGATTCGG", "ATCGGGTTAATACGTGAATTCAGGCTGATCGTGTAGCTTGGATCC")
str_locate_all(my_dna, "GAATTC")

```

## Exercise 2.c:

Let's split the RNA string(below) to their codons (split based on the
spaces).

Next, extract and assign each codon to a different name.

`AAC UCG UGG CCA GAC`

### Solution 2.c:

```{r, results='hide' ,class.source = 'fold-hide'}

codons <- "AAC UCG UGG CCA GAC"
codons <- str_split(codons, pattern = " ")
codons
```

```{r, results='hide' ,class.source = 'fold-hide'}
cod1 <-codons[[1]][1]
cod1
cod2 <-codons[[1]][2]
cod2
cod3 <-codons[[1]][3]
cod3
cod4 <-codons[[1]][4]
cod4
cod5 <-codons[[1]][5]
cod5
```

## Exercise 2.d:

You have a DNA string. How many RE sites did you find? Write a program
which able to simulate the EcorI `GAATTC` EcorI RE function.

`"ACTGATCGATTACGTATAGTAGAATTCTATCATACATTCGATGCGTTCATAC`

`TGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT"`

*Please always check how many restriction enzyme sites exist in the
fragment. `str_count()`*Solution 2.d:

```{r, results='hide' ,class.source = 'fold-hide'}
DNA <- "ACTGATCGATTACGTATAGTAGAATTCTATCATACATTCGATGCGTTCATACTGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT"

str_count(DNA, "GAATTC")

str_split(DNA, "GAATTC")[[1]][1]
FirstSeq <- str_length(str_split(DNA, "GAATTC")[[1]][1])+1
FirstSeq
str_split(DNA, "GAATTC")[[1]][2]
SecondSeq<- str_length(str_split(DNA, "GAATTC")[[1]][2]) + 6
SecondSeq
str_split(DNA, "GAATTC")[[1]][3]
ThirdSeq <- str_length(str_split(DNA, "GAATTC")[[1]][3]) + 5
ThirdSeq
```

## Exercise 2.d:

You have a DNA string. How many RE sites did you find? Write a program
which able to simulate the EcorI `GAATTC` EcorI RE function.

`"ACTGATCGATTACGTATAGTAGAATTCTATCATACATTCGATGCGTTCATAC`

`TGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT"`

*Please always check how many restriction enzyme sites exist in the
fragment. `str_count()`*

### Solution 2.d:

```{r, results='hide' ,class.source = 'fold-hide'}
my_dna <- c("ACTGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT", 
            "ACTTGAATTCTTCAGCTGAGATTCGG", 
            "ATCGGGTTAATACGTGAATTCAGGCTGATCGTGTAGCTTGGATCC")

str_count(my_dna, "GAATTC") #Count number of RE in each string
```

```{r, results='hide' ,class.source = 'fold-hide'}
#Split each DNA string
str_split(my_dna, "GAATTC")
##First DNA
#Split + count the 1st lenght in 1st DNA 
FirstStr_1stDNA <- str_length(str_split(my_dna, "GAATTC")[[1]][1])+1
FirstStr_1stDNA

#Split + count the 2nd lenght in 1st DNA 
ScondStr_1stDNA <- str_length(str_split(my_dna, "GAATTC")[[1]][2]) + 6
ScondStr_1stDNA


##Second DNA
#Split + count the 1st lenght in 2nd DNA 
FirstStr_2ndDNA <- str_length(str_split(my_dna, "GAATTC")[[2]][1])+1
FirstStr_2ndDNA
#Split + count the 2nd lenght in 2nd DNA 
ScondStr_1stDNA <- str_length(str_split(my_dna, "GAATTC")[[2]][2]) + 5
ScondStr_1stDNA


##Third DNA
#Split + count the 1st lenght in 3rd DNA 
FirstStr_3rdDNA <- str_length(str_split(my_dna, "GAATTC")[[3]][1])+1
FirstStr_3rdDNA
#Split + count the 2nd lenght in 3rd DNA 
ScondStr_3rdDNA <- str_length(str_split(my_dna, "GAATTC")[[3]][2]) + 5
ScondStr_3rdDNA

```

## Exercise 2.e:

There are Three sequences of DNA.

How many RE sites did you find? Write a program which able to simulate
the EcorI GAATTC EcorI RE function.

Cut all DNA strings and calculate the length of DNA seq.

`"ACTGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT"`

`"ACTTGAATTCTTCAGCTGAGATTCGG"`

`"ATCGGGTTAATACGTGAATTCAGGCTGATCGTGTAGCTTGGATCC"`

*Please always check how many restriction enzyme sites are exist in the
fragment. `str_count()`*

### Solution 2.e:

```{r, results='hide' ,class.source = 'fold-hide'}
my_dna <- c("ACTGATCGATTACGTATAGTAGAATTCTATCATACATATATATCGATGCGTTCAT", 
            "ACTTGAATTCTTCAGCTGAGATTCGG", 
            "ATCGGGTTAATACGTGAATTCAGGCTGATCGTGTAGCTTGGATCC")

str_count(my_dna, "GAATTC")

str_split(my_dna, pattern = "GAATTC")[[1]][1]            # Extract first string and 1st element
str_length(str_split(my_dna, "GAATTC")[[1]][1])            # Extract first string and 1st element

str_split(my_dna, pattern = "GAATTC")[[1]][2]            # Extract second string and 1st element
str_split(my_dna, pattern = "GAATTC")[[2]][1]            # Extract second string and 1st element
str_split(my_dna, pattern = "GAATTC")[[2]][2]            # Extract second string and 2nd element
```

## Exercise 2.f:

There is a string of DNA. We are interested in selecting locations 9-15
and 22-30. After selecting them, create new strings which include these
two selected strings.

`ACTGATCGATTACGTATAGTATTTGCTATCATACATATATATCGATGCGTTCAT`

### Solution 2.f:

```{r, results='hide' ,class.source = 'fold-hide'}
DNA<- "ACTGATCGATTACGTATAGTATTTGCTATCATACATATATATCGATGCGTTCAT"
A <- str_sub(DNA, 9, 15)
B <- str_sub(DNA, 22, 30)

A
B
str_c(A, B)
```
