---
title: "Day1_Practice"
author: "Molecular Biology and Oncology"
date: "2023-01-03"
output:
  html_document: 
      code_folding: show
---



Preparation:

```{r, results='hide',include=FALSE, class.source = "fold-show"}
library(stringr)
```

## **Exercise 1.a:**

There are Four genetic codons(3 nucleotides). Print them all together and with a semicolon (;) as a separator.

Codon1: "ACG"

Codon2: "CGU"

Codon3: "UUG"

Codon4: "CCG"

##Solution1.a:

```{r, results='hide' ,class.source = 'fold-hide'}
Codon1 <- "ACG"

Codon2 <- "CGU"

Codon3 <- "UUG"

Codon4 <- "CCG"

str_c(Codon1, Codon2, Codon3, Codon4, sep = ";")
```

## Exercise 1.b:

There is a sequence of DNA. This DNA string included how many nucleotides?

`"ACAAGATGCCATTGTCCCCCGGCCTCCTGCTGCTGCTGCTCTCCGGGGCCACGGCCACCGCTGCCCTGCCCCTGGAGG`

`GTGGCCCCACCGGCCGAGACAGCGAGCATATGCAGGAAGCGGCAGGAATAAGGAAAAGCAGCCTCCTGACTTTCCTCGC`

`TTGGTGGTTTGAGTGGACCTCCCAGGCCAGTGCCGGGCCCCTCATAGGAGAGGAAGCTCGGGAGGTGGCCAGGCGGCAG`

`GAAGGCGCACCCCCCCAGCAATCCGCGCGCCGGGACAGAATGCCCTGCAGGAACTTCTTCTGGAAGACCTTCTCCTCCT`

`GCAAATAAAACCTCACCCATGAATGCTCACGCAAGTTTAATTACAGACCTGAA"`

##Solution 1.c:

```{r, results='hide' ,class.source = 'fold-hide'}
DNA <- "ACAAGATGCCATTGTCCCCCGGCCTCCTGCTGCTGCTGCTCTCCGGGGCCACGGCCACCGCTGCCCTGCCCCTGGAGGGTGGCCCCACCGGCCGAGACAGCGAGCATATGCAGGAAGCGGCAGGAATAAGGAAAAGCAGCCTCCTGACTTTCCTCGCTTGGTGGTTTGAGTGGACCTCCCAGGCCAGTGCCGGGCCCCTCATAGGAGAGGAAGCTCGGGAGGTGGCCAGGCGGCAGGAAGGCGCACCCCCCCAGCAATCCGCGCGCCGGGACAGAATGCCCTGCAGGAACTTCTTCTGGAAGACCTTCTCCTCCTGCAAATAAAACCTCACCCATGAATGCTCACGCAAGTTTAATTACAGACCTGAA"


str_length(DNA)
```

## Exercise 1.c:

Use the DNA from Exercise 1c. This DNA string included how many A, U, G, and C?

How many nucleotides are in this DNA string? Write a program that will print out the proportion of A and T content of this DNA sequence.

##Solution 1d:

```{r, results='hide' ,class.source = 'fold-hide'}

A_Counts <- str_count(DNA, "A")
A_Counts
T_Counts <- str_count(DNA, "T")
T_Counts
G_Counts <- str_count(DNA, "G")
G_Counts
C_Counts <- str_count(DNA, "C")
C_Counts
```

```{r, results='hide' ,class.source = 'fold-hide'}
total <- str_length(DNA)
str_c("Number of A in this DNA is", A_Counts)
str_c("Number of T in this DNA is", T_Counts)
# calculating the ratio of A and T in this DNA seq
(A_Counts + T_Counts)/total *100
```

## Exercise 1.e:

You have a DNA string(exercise 1.c.). Write a program to be able to replace U with T.

##Solution 1e:

```{r, results='hide' ,class.source = 'fold-hide'}
str_replace_all(DNA, "T", "U")
```
